Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-02-26 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Some formatting done

      x1 <- c(x1,match(i, cnames2, nomatch = NA)) # MAke a index vector for the location of new_DataFrame col names in template_DataFrame
   }

   new_DataFrame[cnames2[!(cnames2 %in% cnames1)]] <- NA # adding column names to new_DataFrame not in template_DataFrame
   new_DataFrame <- 
      new_DataFrame[,c(cnames2, cnames1[is.na(x1)])]  # adding column names to new_DataFrame not in template_DataFrame
   return(new_DataFrame)
}
source(here("copy_class.R"))
source(here("R/data_mesh.R"))
```

@@

```{r Hermitage_2010}

Herm_10 <-
   as.data.frame(read_xls(here(
      "data/2010 PMmung hermitage RAW field book.xls"),
      sheet = "For analysis"
   ), stringsAsFactors == FALSE)

Herm_10 <- Herm_10 %>%
   mutate(trade_name = case_when(`Schedule!` == "U/S" ~ NA_character_,
                                 `Schedule!` == "FirstsignC" ~ " ",
                                 TRUE ~ "Kendon"))%>%
   mutate(fungicide = case_when(`Schedule!` == "U/S" ~ "control",
                                 `Schedule!` == "FirstsignC" ~ "carbendazim",
                                 TRUE ~ "sulphur"))%>%
   mutate(dose_ai.ha = case_when(`Schedule!` == "U/S" ~ 0,
                                 `Schedule!` == "FirstsignC" ~ 250,
                                 TRUE ~ 2400))%>%
   mutate(fungicide_application_1 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
                                              `Schedule!` == "Early Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
                                              `Schedule!` == "FirstsignC" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
                                              `Schedule!` == "FirstsignS" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
                                              `Schedule!` == "U/S" ~ as.Date(NA),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
                                              `Schedule!` == "Early Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_3 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-05", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_4 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-11", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_5 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_6 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-25", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_7 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-07", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(total_fungicide = case_when(`Schedule!` == "Full Sp" ~ 7,
                                      `Schedule!` == "Early Sp" ~ 2,
                                      `Schedule!` == "FirstsignC" ~ 1,
                                      `Schedule!` == "FirstsignS" ~ 1,
                                      `Schedule!` == "U/S" ~ 0,
                                      TRUE ~ 9999))

@@

```{r Save_PM_MB_means}

>>>>

      x1 <-
         c(x1, match(i, cnames2, nomatch = NA)) # MAke a index vector for the location of new_DataFrame col names in template_DataFrame
   }

   new_DataFrame[cnames2[!(cnames2 %in% cnames1)]] <-
      NA # adding column names to new_DataFrame not in template_DataFrame
   new_DataFrame <-
      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding column names to new_DataFrame not in template_DataFrame
   return(new_DataFrame)
}
source(here("copy_class.R"))
source(here("R/data_mesh.R"))
```

@@

```{r Hermitage_2010}
Herm_10 <-
   as.data.frame(read_xls(here(
      "data/2010 PMmung hermitage RAW field book.xls"
   ),
   sheet = "For analysis"),
   stringsAsFactors == FALSE)

Herm_10 <- Herm_10 %>%
   mutate(
      trade_name = case_when(
         `Schedule!` == "U/S" ~ NA_character_,
         `Schedule!` == "FirstsignC" ~ " ",
         TRUE ~ "Kendon"
      )
   ) %>%
   mutate(
      fungicide = case_when(
         `Schedule!` == "U/S" ~ "control",
         `Schedule!` == "FirstsignC" ~ "carbendazim",
         TRUE ~ "sulphur"
      )
   ) %>%
   mutate(dose_ai.ha = case_when(
      `Schedule!` == "U/S" ~ 0,
      `Schedule!` == "FirstsignC" ~ 250,
      TRUE ~ 2400
   )) %>%
   mutate(
      fungicide_application_1 = case_when(
         `Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
         `Schedule!` == "Early Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
         `Schedule!` == "FirstsignC" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
         `Schedule!` == "FirstsignS" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
         `Schedule!` == "U/S" ~ as.Date(NA),
         TRUE ~ as.Date(NA)
      )
   ) %>%
   mutate(
      fungicide_application_2 = case_when(
         `Schedule!` == "Full Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
         `Schedule!` == "Early Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
         TRUE ~ as.Date(NA)
      )
   ) %>%
   mutate(fungicide_application_3 = case_when(
      `Schedule!` == "Full Sp" ~ as.Date("2010-03-05", format = "%Y-%m-%d"),
      TRUE ~ as.Date(NA)
   )) %>%
   mutate(fungicide_application_4 = case_when(
      `Schedule!` == "Full Sp" ~ as.Date("2010-03-11", format = "%Y-%m-%d"),
      TRUE ~ as.Date(NA)
   )) %>%
   mutate(fungicide_application_5 = case_when(
      `Schedule!` == "Full Sp" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
      TRUE ~ as.Date(NA)
   )) %>%
   mutate(fungicide_application_6 = case_when(
      `Schedule!` == "Full Sp" ~ as.Date("2010-03-25", format = "%Y-%m-%d"),
      TRUE ~ as.Date(NA)
   )) %>%
   mutate(fungicide_application_7 = case_when(
      `Schedule!` == "Full Sp" ~ as.Date("2010-03-07", format = "%Y-%m-%d"),
      TRUE ~ as.Date(NA)
   )) %>%
   mutate(
      total_fungicide = case_when(
         `Schedule!` == "Full Sp" ~ 7,
         `Schedule!` == "Early Sp" ~ 2,
         `Schedule!` == "FirstsignC" ~ 1,
         `Schedule!` == "FirstsignS" ~ 1,
         `Schedule!` == "U/S" ~ 0,
         TRUE ~ 9999
      )
   )

@@

```{r Save_PM_MB_means, eval=FALSE, include=FALSE}
